BurgerTown Presents: Open Adcess

### 2017-04-23 paper-sponsorships.tex
typos

\paragraph{Dropped Packets}
Dropped Packets serves as the traditional missed connections section of the
classifieds. While this could be used to contact that cutie from the latest
While this could be used to contact that cutie from the latest conference, we
believe that it could also be used to publicly shame those who miss meetings.

Sample: Missed Connection: Lost Tofutti Cutie at last conference, fell behind the freezer before I could read it. No reward. I just want a witness to my experience.

Sample: ``Damn it Deborah, you were supposed to bring bagels to the DARPA
Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}
(DTA\censor{b}HBI\censor{bb}) meeting!"
Sample: I was hiding in your closet at 54 Bishop Allen Dr. \# 2 and you were home and you took a shower but you grabbed wrinkled clothes from your laundry hamper and didn't access your closet, and I hadn't eaten anything but moths for many hours, so I slipped out of your home but just know you are loved.

>>>>

\paragraph{Dropped Packets}
Dropped Packets serves as the traditional missed connections section of the
classifieds.
While this could be used to contact that cutie from the latest conference, we
believe that it could also be used to publicly shame those who miss meetings.
Some examples include:

\begin{enumerate}
  \item Missed Connection: Lost Tofutti Cutie at last conference, fell behind the freezer before I could read it. No reward. I just want a witness to my experience.

  \item Damn it Deborah, you were supposed to bring bagels to the DARPA
Tactical Anti-\censor{blank} HAVE BAGEL Infiltration \censor{long blank}
(DTA\censor{b}HBI\censor{bb}) meeting!

  \item I was hiding in your closet at 54 Bishop Allen Dr. \# 2 and you were home and you took a shower but you grabbed wrinkled clothes from your laundry hamper and didn't access your closet, and I hadn't eaten anything but moths for many hours, so I slipped out of your home but just know you are loved.
\end{enumerate}
